We kind of need a title

### 2020-03-09 paper.tex
Merged James' changes

	\section{Basics of Artificial Intelligence}\label{introtoai}
		Artificial intelligence (AI) in its basic form is a computer program that takes in an input or inputs and produces an output. An example of a procedural AI would be a program that took in how many hours it had been since someone showered and determined whether they were due for a shower or not. The AI would have a threshold that would trigger a recommendation to shower. For the purpose of this example we will set it at twenty-four hours. If it had been sixteen hours since someone showered, it would not tell them to shower, but if it had been twenty-seven hours since they showered, the AI would recommend a shower. However, we know time is not the only factor in whether someone should shower. To better improve this theoretical AI, a second input could be added such as whether the person had showered since their last shower. In general, people should shower after they exercise. The updated logic in the AI is that it will recommend a shower if the time since the last shower is greater than twenty-four hours or if they have exercised since their last shower. Only one condition has to be true to recommend a shower, but both could be true. The more inputs or parameters that the AI takes in the better it will get a giving a correct output as long the researcher determined the correct thresholds for the AI.

		Eventually as the AI gets more complex, two problems present themselves. First, not all problems that an AI tries to solve has a simple linear relation between their inputs and the output. Second, the researcher may not know the exact relation between the inputs and the output. This is where a subset of AI called Machine Learning (ML) comes into play. Neural networking, a method of ML, crudely simulates a brain. The way the brain works is it has many neurons that are connected together by synapses.

@@

>>>>

	\section{Basics of Artificial Intelligence}\label{introtoai}
		Artificial Intelligence (AI) in its basic form is a computer program that takes in an input or inputs and produces an output.  An example would be if a program took in how many hours it had been since someone washed their hands and determined whether they were due for washing their hands or not  The AI would have a threshold that would trigger a recommendation to shower.  For the purpose of this example, we will set it at two hours.  If it had been half an hour since someone washed their hands, it would not tell them to wash their hands, but if it had been five hours since they washed their hands, the AI would recommend washing their hands.  However, we know time is not the only factor in whether someone should wash their hands.  To better improve this theoretical AI, a second input could be added such as whether the person is about to touch or consume food.  In general, people should wash their hands if they are about touch or consume food.  The updated logic in the AI is that it will recommend a washing hands if the time since the last time someone washed their hands is greater than two hours or if they are about to touch or consume food. Only one condition has to be true to recommend a washing hands, but both could be true.  The more inputs or parameters that the AI takes in the better it will get a giving a correct output as long the researcher determined the correct thresholds for the AI.

		Eventually as the AI gets more complex, two problems present themselves.  First, not all problems that an AI tries to solve has a simple linear relation between their inputs and the output.  Second, the researcher may not know the exact relation between the inputs and the output.  This is where a subset of AI called Machine Learning (ML) comes into play.  A common type of  ML is called a Neural Network (NN) which more or less simulates a brain to a far lesser extent.  The way the brain works is it has many neurons that are connected together by axons and synapses. Axons are used to transport the electrical signals for the neurons. Synapses receive the signals at the end of the axons. Each synapse has a strength that determines how important the signal matters whether from another neuron or an input from the body. A neuron can have multiple inputs. The neuron sums all the signals with some mattering more than the others based on their synaptic strength. Once the neuron reaches a certain sum, it fires sending signals to other neurons or the body. The synaptic strengths can be changed over time based on whether the response generated by the neurons was correct for whatever situation. Over time, the synaptic strengths for a neuron are optimized to provide a correct response most of the time. Neural Networks work in a similar way. Each NN has nodes and weights. Nodes are like the neurons in the brain and weights are like the synaptic strength. The most basic NN has two layers. A layer of input nodes that takes the inputs in and passes them onto the next layer, the output layer. The hidden layer takes in the input, multiplies them by their weights, and sums them. An activation function maps the sum of the adjusted inputs to the desired output. The way the NN is trained through using data with known inputs and outputs. An algorithm known as error backpropagation is used to adjust the weights. In simple terms, it compares the output using the current weights, compares it to the desired output, and adjusts the weights until there is a little to no error. The example of washing hands can also be modeled with a NN. It would have two input nodes. One would take in the number of hours since someone had washed their hands and the other would take in whether someone was about to touch or consume food. The input nodes send the inputs to the output node where the inputs would be multiplied by their weights and summed. At first the weights would be randomly assigned or assigned to an estimate based off of previous knowledge of the researcher. An activation function would then be used to turn the sum into a yes or no of whether someone should wash their hands. Training data with known inputs and outputs would be used with error back propagation to adjust the weights until the error was eliminated. More inputs can also be added to improve the NN, but the real power of NN comes by adding a layer or layers between the input and output layers. Nodes can also be added to these layers. The more nodes the better. Once there is more than one layer, the connections between the nodes of separate layers can be chosen. The nodes of the previous layer do not have to connect to all the nodes of the next layer. More layers, nodes, and connections will make the NN better, but as the complexity increases, the time that it takes for the NN to produce an output increases. At a certain point of adding layers, nodes, and connections, the improvement of the success rate will be marginal in comparison with increase in time to run the NN. Neural Networks are used to model nonlinear problems linearly which can be very useful in the medical field.

@@

		In their book Principles of Biomedical Ethics, Beauchamp and Childress outline four principles: autonomy, beneficence, nonmaleficence, and justice. Each principle is used to help medical profesional make decisions on treating patients.

		The first principle autonomy refers to the ability to decide for oneself free from control of others and with sufficient level of understanding as to provide for meaningful choice. Also, the person deciding should have capacity to make the choice. Next, beneficence is the principle of weighing the risks against benefits in order to get the best result. This applies to not only the patient, but it also applies to society in general. The benefits to society should be considered when weighing the risks. Nonmaleficence can be summed up with primum non nocere, first do no harm. A medical professional should do no harm. Finally, justice addresses the question of who receives healthcare resources as they are in sarces supply.
